Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-08-02 doc/PRF2022/PRF_main.tex
yny

\section{Introduction}
% Put \label in argument of \section for cross-referencing
%\section{\label{}}
Janus particles are colloids whose surfaces 
%have different properties. For example, it is common for the surface of a Janus
%particle to be 
may be partly hydrophilic and hydrophobic (polar and non-polar).
More generally the surface of a Janus particle may have a spatial distribution of hydrophobicity/hydrophilicity.
In the absence of any imposed flow, Janus particles often self-assemble into
structures in a viscous solvent with tunable functions for biomedical engineering
applications~\cite{GheisariSahfieeAbbasiEtAl2021_DMR,
LiuYangHuangEtAl2016_Angew, LiWangYaoEtAl2019_Nanoscale, Bradley2016}.
Depending on the interactions between Janus particles (JPs) and the
surrounding viscous solvent, JPs self-assemble into oligomers of various
geometries and sizes~\cite{Bradley2017}.

@@

The many-body hydrodynamics of amphiphilic Janus particles assembled as
vesicles suspended in a viscous fluid (at zero Reynolds number) has
been studied using boundary integral numerical
simulations~\cite{Fu20,Fu2022_JFM}. The dynamics of the JP suspension
results from the combination of long-range hydrodynamic interaction and
non-local interactions between JPs through the distribution of a
hydrophobic attraction potential (HAP).
%
In a quiescent flow, numerical simulations of a JP suspension showed
self-assembly into micelles and bilayers of JPs that provide an
alternative means for computing the mechanical moduli of a colloidal
membrane~\cite{NaTr00,Fu20,KrFiGuKaHa13}. Under background flows, the
hydrodynamics of a JP vesicle (a self-enclosed bilayer of JPs) exhibit
many familiar behaviors of a vesicle: elongation and
alignment along the extensional direction, tank-treading, and rupture of
a vesicle under shear flow~\cite{Fu2022_JFM}.

In this work, we take advantage of the flexibility of the model to
examine the effects of boundary condition on JP surfaces that could be
controlled based on the chemicals used in the experiments, for example.
We show that a simple tuning of the hydrophobic distribution leads to
multilamellar and striated structures. Here, less is understood about the
flow-structure interactions and we investigate the deformation of these
novel materials in background flows and map out their collective
behavior away from equilibrium.

>>>>

\section{Introduction}
% Put \label in argument of \section for cross-referencing
%\section{\label{}}
Janus particles are colloids whose surfaces 
%have different properties. For example, it is common for the surface of a Janus
%particle to be 
are partly hydrophilic and hydrophobic (polar and non-polar).
More generally the surface of a Janus particle may have a spatial distribution of hydrophobicity/hydrophilicity.
In the absence of any imposed flow, Janus particles often self-assemble into
structures in a viscous solvent with tunable functions for biomedical engineering
applications~\cite{GheisariSahfieeAbbasiEtAl2021_DMR,
LiuYangHuangEtAl2016_Angew, LiWangYaoEtAl2019_Nanoscale, Bradley2016}.
Depending on the interactions between Janus particles (JPs) and the
surrounding viscous solvent, JPs self-assemble into oligomers of various
geometries and sizes~\cite{Bradley2017}.

@@

The many-body hydrodynamics of amphiphilic Janus particles assembled as
vesicles suspended in a viscous fluid in the inertialess regime (zero Reynolds number) has
been studied using boundary integral numerical
simulations~\cite{Fu20,Fu2022_JFM}. The dynamics of the JP suspension
results from the combination of long-range hydrodynamic interaction and
non-local interactions between JPs through the distribution of a
hydrophobic attraction potential (HAP).
%
In a quiescent flow, numerical simulations of a JP suspension showed
self-assembly into micelles and bilayers of JPs that provide an
alternative means for computing the mechanical moduli of a colloidal
membrane~\cite{NaTr00,Fu20,KrFiGuKaHa13}. Under background flows, the
hydrodynamics of a JP vesicle (a self-enclosed bilayer of JPs) exhibit
many familiar behaviors of a vesicle: elongation and
alignment along the extensional direction, tank-treading, and rupture of
a vesicle under shear flow~\cite{Fu2022_JFM}.

In this work, we take advantage of the flexibility of the HAP model to
examine the effects of varying hydrophobicity/hydrophilicity on JP surfaces.
Such variation of the boundary condition on JP surfaces may be realized in the experiments by using
chemicals to adjust the polarity of the viscous solvent, for example ({\bf references needed here}).
We show that a simple tuning of the hydrophobic distribution leads to transitions from unilamellar to
multilamellar or striated structures. 
Focusing on the fluid-structure interactions that correspond to such transitions, 
we investigate the deformation of these
novel structures in background flows and map out their collective
behavior away from equilibrium.
